---
title: "What Skills Do Remote Tech Employers Actually Want?"
date: 2026-09-14
Writer: Yuzhuo Cui
---

## Introduction

This post uses web scraping to collect 25 recent remote tech job postings from
[We Work Remotely](https://weworkremotely.com) and analyzes the full
job descriptions to identify which technical skills appear most often.

The goal is not just to demonstrate scraping, but to answer a practical
question: **if you are preparing for a remote tech career, what should
you learn first?**

## Data Collection

I used the `rvest` package in R to parse the public RSS feed from
We Work Remotely's programming jobs category. 

```{r}
#| message: false
#| warning: false

library(rvest)
library(dplyr)
library(tibble)
library(stringr)
library(purrr)
library(ggplot2)

url <- "https://weworkremotely.com/categories/remote-programming-jobs.rss"
page <- read_html(url)
items <- page %>% html_elements("item")

length(items)
```
There are 25 job postings for the research.  

## Data Cleaning

Each RSS `<item>` contains a title, region, category, publication date,
and a full job description. I extracted all five fields into a tidy
data frame.

```{r}
titles       <- items %>% html_element("title") %>% html_text2()
regions      <- items %>% html_element("region") %>% html_text2()
categories   <- items %>% html_element("category") %>% html_text2()
dates        <- items %>% html_element("pubdate") %>% html_text2()
descriptions <- items %>% html_element("description") %>% html_text2()

jobs <- tibble(
  title       = titles,
  region      = regions,
  category    = categories,
  date        = dates,
  description = descriptions
)

glimpse(jobs)
```

## Analysis

I defined a list of 30 common technical skills and counted how many
job descriptions mention each one. I used word-boundary regex
(`\\b`) to avoid false matches — for example, ensuring that "Java"
does not match "JavaScript", and that "AI" does not match "email".

```{r}
skills_list <- c(
  "Python", "JavaScript", "TypeScript", "Java", "Golang",
  "React", "Vue", "Angular", "Node", "Django", "Flask",
  "SQL", "PostgreSQL", "MySQL", "MongoDB",
  "AWS", "Azure", "GCP", "Docker", "Kubernetes",
  "Git", "CI/CD", "GraphQL",
  "Machine Learning", "TensorFlow", "PyTorch",
  "HTML", "CSS", "Linux", "Bash"
)

skill_counts <- tibble(
  skill = skills_list,
  n = map_int(skills_list, function(s) {
    sum(str_detect(jobs$description,
                   regex(paste0("\\b", s, "\\b"), ignore_case = TRUE)))
  })
) |>
  filter(n > 0) |>
  arrange(desc(n))

print(skill_counts, n = 30)
```

```{r}
#| fig-cap: "Most in-demand technical skills in remote tech jobs"
#| fig-width: 8
#| fig-height: 6

skill_counts |>
  mutate(skill = reorder(skill, n)) |>
  ggplot(aes(x = n, y = skill)) +
  geom_col(fill = "#2c7fb8") +
  geom_text(aes(label = n), hjust = -0.3, size = 4) +
  labs(
    title = "Most In-Demand Technical Skills in Remote Jobs",
    subtitle = "Based on 25 job postings from We Work Remotely",
    x = "Number of postings mentioning this skill",
    y = NULL,
    caption = "Data source: We Work Remotely (https://weworkremotely.com)"
  ) +
  theme_minimal(base_size = 13) +
  expand_limits(x = max(skill_counts$n) * 1.2)
```

## Key Findings

**1. Frontend frameworks lead the pack.**
React appears in 10 out of 25 postings (40%) — more than any other
skill. This confirms that modern remote employers expect engineers
to be comfortable building interactive user interfaces.

**2. Cloud and DevOps skills are the new baseline.**
AWS (9), CI/CD (8), Docker (7), and Kubernetes (5) together appear
in over 60% of postings. Cloud infrastructure and automated
deployment are common expectations for remote engineers.

**3. Data and database skills are less expected.**
MongoDB (4), PostgreSQL (2), and SQL (1) appear less frequently comparing to other skills.

## Actionable Recommendation

**If you are preparing for a remote tech career, prioritize:**

1. **React** — it appears in 40% of postings and is the single most
   requested skill.
2. **AWS + Docker + CI/CD** — this trio of cloud and DevOps skills
   appears across more than half of the postings.
3. **Python** — the most transferable language, useful for backend,
   data analysis, and machine learning roles.


## Limitations

This analysis covers only 25 postings from a single RSS feed at one
point in time. We Work Remotely is not representative of all remote
work, and counting keywords in job descriptions is a rough proxy for
skill demand. 

## Data Source

All data was collected from [We Work Remotely](https://weworkremotely.com).
The RSS feed is publicly available and does not require authentication.